---
title: "Actividad Naive Bayes FCI"
output: 
 html_document:
    collapse: true
    smooth_scroll: true
    theme: journal
    highlight: kate
    df_print: paged
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#Carga de librerías
library(e1071)
library(caret)

datos <- data.frame(
  TiempoEstudio = factor(c("Alto", "Medio", "Bajo", "Alto", "Medio", "Alto", "Bajo", "Medio", "Alto", "Bajo",
                           "Alto", "Bajo", "Medio", "Alto", "Medio", "Bajo", "Alto", "Alto", "Medio", "Bajo",
                           "Medio", "Alto", "Bajo", "Medio", "Alto")),
  Asistencia = factor(c("Alta", "Media", "Baja", "Alta", "Media", "Alta", "Baja", "Alta", "Media", "Baja",
                        "Alta", "Baja", "Media", "Alta", "Alta", "Baja", "Alta", "Media", "Alta", "Baja",
                        "Media", "Alta", "Baja", "Media", "Alta")),
  Participacion = factor(c("Alta", "Baja", "Baja", "Media", "Media", "Alta", "Baja", "Media", "Alta", "Media",
                           "Alta", "Baja", "Media", "Alta", "Media", "Baja", "Alta", "Alta", "Media", "Baja",
                           "Media", "Alta", "Baja", "Media", "Alta")),
  SituacionEcon = factor(c("Buena", "Mala", "Mala", "Buena", "Buena", "Buena", "Mala", "Buena", "Buena", "Mala",
                           "Buena", "Mala", "Buena", "Buena", "Buena", "Mala", "Buena", "Buena", "Buena", "Mala",
                           "Buena", "Buena", "Mala", "Buena", "Buena")),
  Rendimiento = factor(c("Excelente", "Regular", "Deficiente", "Bueno", "Bueno", "Excelente", "Deficiente", "Bueno", "Excelente", "Regular",
                         "Excelente", "Deficiente", "Bueno", "Excelente", "Bueno", "Deficiente", "Excelente", "Excelente", "Bueno", "Deficiente",
                         "Bueno", "Excelente", "Deficiente", "Bueno", "Excelente"))
)

#División 80/20
set.seed(123)
index <- createDataPartition(datos$Rendimiento, p = 0.8, list = FALSE)
train <- datos[index, ]
test <- datos[-index, ]

# Modelo
modelo_nb <- naiveBayes(Rendimiento ~ ., data = train)
modelo_nb

# Predicción
preds <- predict(modelo_nb, test)

# Matriz de confusión
confusionMatrix(preds, test$Rendimiento)